Category-Pivot Transfer Learning from Knowledge Base to Microblog Stream for Accurate Event Detection

### 2016-10-02 paper/lncsFormat.tex
finish 3.3.2.3, and 5200 words

Given (word, category) time series and microblogs in a time window, we take the detection in	 three sub-phases: (1) detecting events' candidate words; (2) generating event phrases; (3) linking event tweets with event phrases.
%这里添加对这几个Definition的解释。

@@

In order to group the bursty words together, we  construct the directed weighted graph \(\mathcal{G}_{c,t}=(\mathcal{B}_{c,t},\mathcal{E}_{c,t})\), where \(\mathcal{E}_{c,t}=\{(a,b,PMI(a,b))|a \in \mathcal{B}_{c,t}, b \in \mathcal{B}_{c,t}, PMI(a,b)>0 \}\). 
The graph \(\mathcal{G}_{c,t}\) means the words in \(\mathcal{B}_{c,t}\) are connected if and only if their PMI score in the given time window's microblogs is over 0.

>>>>

Given (word, category) time series and microblogs in a time window, we take the detection in	 three sub-phases: (1) detecting events' candidate words; (2) generating event phrases; (3) linking event tweets with event phrases.
Note that these sub-phases are also available for the common text stream, but they performs better when words are enriched by category concepts of knowledge base.
%这里添加对这几个Definition的解释。

@@

In order to group the bursty words together, we  construct the directed weighted graph \(\mathcal{G}_{c,t}=(\mathcal{B}_{c,t},\mathcal{E}_{c,t},\mathcal{W}_{c,t})\), where \(\mathcal{E}_{c,t}=\{(a,b)|a \in \mathcal{B}_{c,t}, b \in \mathcal{B}_{c,t}, PMI(a,b)>0 \}\), and \(\mathcal{W}_{c,t}\) gives the PMI scores on the edges.
The graph \(\mathcal{G}_{c,t}\) means the words in \(\mathcal{B}_{c,t}\) are connected if and only if their PMI score in the given time window's microblogs is over 0.

Given the graph \(\mathcal{G}_{c,t}\), spectral clustering\cite{von2007tutorial} is utilized for exploring the best partition of words. 
To get the optimum cluster number, we use the graph density as the criteria.
The graph density is the ratio of the number of edges to that of complete graph (the graph with all possible edges), and in practice all the sub-graphs in \(\mathcal{G}_{c,t}\) should have the densities over an empirical threshold. 
We run the spectral clustering with cluster number from 1 to \(|\mathcal{B}_{c,t}|\), and stop when all the resulting sub-graphs satisfy the criteria that the density is over the given threshold. 
In this way, the generated event phrase combines the co-occurred bursty words and excludes the unrelated.
